---
title: "Homework 28"
format: html
editor: visual
---

# Homework 28: Pimping Your Plots

Normal code set up:

```{r}
rm(list = ls())
library(tidyverse)
library(here)
library(gridExtra)
```

Read in the Data

```{r}
comp <- read.csv(here("data", "compensation.csv"))
```

## Preparation 

Make a scatterplot and a box plot and assign them to an object for future use

```{r}
eg_scatter <- ggplot(data = comp, aes(x = Root, y = Fruit)) + 
  geom_point()

eg_box <- ggplot(data = comp, aes(x = Grazing, y = Fruit)) + 
  geom_boxplot()
```

Use the saved figures and add `theme_bw()` to the scatterplot

```{r}
eg_scatter + theme_bw()
```

Use `grid.arrange()` to put the scatter plot and box plot on the same page

```{r}
grid.arrange(eg_box, eg_scatter, nrow = 1)
```

## Axis Labels, Limits and Annotations

Change the labels on the scatter plot

```{r}
eg_scatter + 
  xlab("Root Biomass") + 
  ylab("Fruit Production") + 
  ggtitle("My SUPERB Title") # Way to add a title, although when would you really need one?

# Combine all of the labels under the labs() function
eg_scatter + labs( x = "Root Biomass", y = "Fruit Production", title = "My useless Title")
```

Change the range on the x and y-axis

```{r}
eg_scatter + 
  xlim(0,20) + 
  ylim(0,140)
```

Put custom text inside the figure

```{r}
eg_scatter + 
  annotate("text", x = c(6,8), y = c(105,25), label = c("text up here ...", "... and text down here"))
```

## Scales

Adjust range using the `limit =` argument

```{r}
eg_scatter + 
  scale_x_continuous(limits = c(4,11), breaks = c(4:11))
```

Now use `scale()` to customize the colors

```{r}
ggplot(data = comp, aes(x = Root, y = Fruit, color = Grazing)) + 
  geom_point() + 
  scale_color_manual(values = c(Grazed = "brown", Ungrazed = "darkgreen"))
```

Change the y-axis scale to a log scale

```{r}
eg_box + 
  scale_y_continuous(breaks = seq(from = 10, to = 150, by = 20), trans = "log10")
```

## Customize the Theme

```{r}
eg_scatter + 
  theme(
    panel.background = element_rect(fill = NA, color = "black"), # white background, black border
    panel.grid.minor = element_blank(), # no minor grid lines
    panel.grid.major = element_line(color = "lightblue") #add major grid lines and change color
  )
```

Manipulate the color, position, and size of axis title

```{r}
eg_box + 
  theme(
    axis.title.x = element_text(color = "cornflowerblue", 
                                size = rel(2)), 
    axis.text.x = element_text(angle = 45, size = 13, vjust = 0.5))
```

Change the names of the levels on the graph

```{r}
eg_box + 
  scale_x_discrete(limits = c("Ungrazed", "Grazed"), labels = c("Control", "Grazed"))
```

Customizing legend/key

```{r}
ggplot(comp, aes(x = Root, y = Fruit, color = Grazing)) + 
  geom_point() + 
  theme(legend.key = element_rect(fill = NA))
```

Get rid of the legend

```{r}
ggplot(comp, aes(x = Root, y = Fruit, color = Grazing)) + 
  geom_point() +
  theme(legend.position = "none")
```
