---
title: "Homework 21"
format: html
editor: visual
---

Normal set up

```{r}
rm(list = ls())
library(tidyverse)
library(here)
```

Read in the data

```{r}
lady <- read.csv(here("data", "ladybirds.csv"))
ozone <- read.csv(here("data", "ozone.csv"))
```

## Chi-squared analysis

Look at the data

```{r}
glimpse(lady)
```

Calculate totals

```{r}
totals <- lady |>
  group_by(Habitat, colour) |>
  summarize(total.number = sum(number))
```

Make a bar chart to summarize data

```{r}
ggplot(totals, aes(x = Habitat, y = total.number, fill = colour)) + 
  geom_bar(stat = "identity", position = "dodge") + # plot with basic colors
  scale_fill_manual(values = c(black = "black", red = "red")) # make bars the desired colors
```

Use the xtabs() function to transform the data into a matrix for the chi squared test

```{r}
lady.mat <- xtabs(number ~ Habitat + colour, data = lady)

lady.mat
```

Do the actual chi squared test

```{r}
chisq.test(lady.mat)
```

Assign a name to the chi squared test to see the Yates' comtinuity correction

```{r}
lady.chi <- chisq.test(lady.mat)
names(lady.chi)

lady.chi$expected
```

## Two Sample T-test

look at the ozone data

```{r}
glimpse(ozone)
```

Make a hsitogram

```{r}
ggplot(ozone, aes(x = Ozone)) + 
  geom_histogram(binwidth = 10) + 
  facet_wrap(~ Garden.location, ncol = 1) + 
  theme_bw()
```

do the t-test

```{r}
t.test(Ozone ~ Garden.location, data = ozone)
```

Var.test has the same structure as the t-test

```{r}
var.test(Ozone ~ Garden.location, data = ozone)
```
