---
title: "Homework 26"
format: html
editor: visual
---

**Normal Set Up**

```{r}
rm(list = ls())
library(tidyverse)
library(here)
library(ggfortify)
library(multcomp)
```

**Read in the data**

```{r}
peas <- read.csv(here("data", "s_r_pea_sections.csv"))
```

**Make `Treatment` a factor variable**

```{r}
peas$Treatment <- as.factor(peas$Treatment)
levels(peas$Treatment)
```

**Plot and estimate results**

```{r}
ggplot(peas, aes(x = Treatment, y = pea_section_length_ou)) +
  geom_boxplot()+
  geom_point() +
  theme_bw()

```

I would expect to find that there is a difference between the control group and the treatment groups, as well as a difference between the 2% sucrose group and the other groups, but no difference between the other treatment groups.

**Build the model**

```{r}
pea_model <- lm(pea_section_length_ou ~ Treatment, data = peas)
```

**Check Assumptions**

```{r}
autoplot(pea_model, smooth.colour = NA)
```

Looks fine

**Make ANOVA and Summary tables**

```{r}
anova(pea_model)
```

```{r}
summary(pea_model)
```

Looks like there is a significant difference between the treatment groups and the control group, but which ones are different from each other? F 4, 45 = 49.368, p \< 0.01

**Conduct Tukey HSD**

```{r}
phc1 <- glht(pea_model, linfct = mcp(Treatment = "Tukey"))
summary(phc1)
```

**Do the compact letter display**

```{r}
cld(phc1)
```

There is a significant difference between the control group and the rest of the treatment groups, and between the 2% sucrose group and all of the other groups. There is no significant difference between 1% fructose 1% glucose, 2% fructose, and 2% glucose.
