---
title: "Homework 16"
format: html
editor: visual
---

Normal set up. Add code to clear R's brain and load in the tidyverse and here packages
```{r}
rm(list = ls())
library(tidyverse)
library(here)
```

Read in donnerville percent cover .csv
```{r}
cover <- read.csv(here("data", "donnerville_percent_cover.csv"))
```

Examine the data
```{r}
glimpse(cover)
str(cover)
```

Turn site, plot type, and cover_type into factor variables
```{r}
cover$Site <- as.factor(cover$Site)
cover$Plot.type <- as.factor(cover$Plot.type)
cover$cover_type <- as.factor(cover$cover_type)
levels(cover$Site)
levels(cover$Plot.type)
levels(cover$cover_type)
```

Fix the site and cover_type variables
```{r}
fix1 <- which(cover$Site %in% c("DONNERVILLE - 1","donnerville 1","Donnerville 1"))
cover$Site[fix1] <- "donnerville 1"
cover$Site <- factor(cover$Site)
```

```{r}
fix2 <- which(cover$Site %in% c("donnerville 2", "Donnerville 2"))
cover$Site[fix2] <- "donnerville 2"
cover$Site <- factor(cover$Site)
```

```{r}
fix3<- which(cover$Site %in% c("Donnerville 3", "donnerville-3"))
cover$Site[fix3] <- "Donnerville 3"
cover$Site <- factor(cover$Site)
```

```{r}
fix4 <- which(cover$cover_type %in% c("bare", "Bare"))
cover$cover_type[fix4] <- "Bare"
cover$cover_type <- factor(cover$cover_type)
```

```{r}
fix5 <- which(cover$cover_type %in% c("bryophtes", "Bryophytes"))
cover$cover_type[fix4] <- "Bryophytes"
cover$cover_type <- factor(cover$cover_type)
```

```{r}
fix6 <- which(cover$cover_type %in% c("vasc", "Vascular"))
cover$cover_type[fix4] <- "Vascular"
cover$cover_type <- factor(cover$cover_type)
```

Turn Date into a date variable in R
```{r}
cover$Date <- dmy(cover$Date)
```

Determine average percent cover by type
```{r}

```

Determine average percent vascular plant cover across all sites 
```{r}

```

