---
title: "Homework 24"
format: html
editor: visual
---

## Overview

For your homework you will implement a data analysis using a dataset on crab growth measurements.

Set things up (hint: there is a new package to add with `library()`)

```{r}
rm(list = ls())
library(tidyverse)
library(here)
library(ggfortify)
```

## The data

Let's pull in some data appropriate biologists: crab measurements. This dataset includes measurements of farmed crabs.

```{r}
crabs <- read.csv(here("data", "CrabAgePrediction.csv"))
glimpse(crabs)
```

One of the variables is categorical - let's fix that in the data.

```{r}
crabs$Sex <- as.factor(crabs$Sex)
levels(crabs$Sex)
```

## Question

Is there a relationship between height and weight in female crabs?

1.  Extract the data for just female crabs.

```{r}
females <- crabs |> 
  filter(Sex == "F", Height < 2, Height > 0.1) # Without outliers

females_out <- crabs |> 
  filter(Sex == "F")
```

2.  Examine the response and predictor variables and use the flow chart from class to decide the appropriate statistical analysis (choose from: chi-square, 2-sample t-test or linear regression). Explain your answer here: Doing a regression because predictor and response variables are continuous and we are testing for a relationship between the predictor and response variables.
3.  Work through the data analysis **following all of the steps provided in chapter 5 of your book**. You may use class notes or homework keys as a guide.

Step 1: make a scatter plot

```{r}
#Without outliers
ggplot(females, aes(x = Height, y = Weight)) +
  geom_point() + 
  theme_bw()
#Looks like there is a strong positive linear relationship between height and weight

#with outliers 
ggplot(females_out, aes(x = Height, y = Weight)) +
  geom_point() + 
  theme_bw()
```

estimate slope and intercept from figure

Step 2: Fit a linear model

```{r}
#Without outliers
crab_model <- lm(Weight ~ Height, data = females)

#With outliers
crab_model_out <- lm(Weight ~ Height, data = females_out)
```

Step 3: Check assumptions

```{r}
#Without outliers
autoplot(crab_model, smooth.colour = NA)


#with outliers
autoplot(crab_model_out, smooth.colour = NA)
#looks weird
```

Data normally distributed (Normal QQ)

Equal variance (scale-location)

good linear fit (residuals vs fitted)

influence of outliers (residuals vs leverage)

Step 4: get ANOVA table for sum of squares

```{r}
# outliers removed
anova(crab_model)

# Has outliers
anova(crab_model_out)
```

Make a summary table

```{r}
summary(crab_model) # no outliers
summary(crab_model_out) # outliers
```

The P-value is 2.2X10\^-16 which indicates that height is a statistically significant predictor of the height of crabs, whether or not the outliers are included. Slope is significantly different from 0
