---
title: "Homework 18"
format: html
editor: visual
---

Normal Set up

```{r}
rm(list = ls())
library(tidyverse)
library(here)
```

Read in compensation.csv

```{r}
comp <- read.csv(here("data", "compensation.csv"))
```

## Scatter plots ##

Create a simple bivariate scatter plot of the data

```{r}
ggplot(comp, aes(x = Root, y = Fruit)) + 
  geom_point()
# tell it the data frame you want, then aes() defines the graphs features and then add a geometric layer as the points
```

Get rid of the grey background

```{r}
ggplot(comp, aes(x=Root, y=Fruit)) + 
  geom_point() + 
  theme_bw() #black and white theme
```

Increase point size

```{r}
ggplot(comp, aes(x=Root, y=Fruit)) + 
  geom_point(size = 5) + # make point size 5
  theme_bw()
```

Add axis labels

```{r}
ggplot(comp, aes(x=Root, y=Fruit)) + 
  geom_point() + 
  xlab("Root Biomass") + #x-axis label 
  ylab("Fruit Production") + #y-axis label
  theme_bw()
```

Adjust the color of the points to match levels in a group
```{r}
ggplot(comp, aes(x=Root, y=Fruit, color = Grazing)) + #change color based on grazing
  geom_point(size = 5) + 
  xlab("Root Biomass") +
  ylab("Fruit Production") + 
  theme_bw()
```

Change the shape to match levels in a group

```{r}
ggplot(comp, aes(x=Root, y=Fruit, shape = Grazing)) + #change shape based on grazing
  geom_point() + 
  xlab("Root Biomass") +
  ylab("Fruit Production") + 
  theme_bw()
```

## Box and Whisker Plots

Basic box and whisker plot
```{r}
ggplot(comp, aes(x=Grazing, y=Fruit)) + 
  geom_boxplot() + 
  xlab("Grazing Treatment") +
  ylab("Fruit Production") + 
  theme_bw()
```

Add a layer for the raw data
```{r}
ggplot(comp, aes(x=Grazing, y=Fruit)) + 
  geom_boxplot() +
  geom_point(size = 4, color = 'lightgrey', alpha = 0.5 ) + # adds points to the plot
  xlab("Grazing Treatment") +
  ylab("Fruit Production") + 
  theme_bw()
```

## Histograms

basic histogram of fruit production
```{r}
ggplot(comp, aes(x=Fruit)) +
  geom_histogram()
#makes an ugly plot
```

Change the binwidth
```{r}
ggplot(comp, aes(x = Fruit)) + 
  geom_histogram(bins = 10) #change the number of bins
ggplot(comp, aes(x = Fruit)) + 
  geom_histogram(binwidth = 15) # change the binwidth (how wide the bars are)
```

Separate histograms by levels in a group
```{r}
ggplot(comp, aes(x = Fruit)) + 
  geom_histogram(binwidth = 15) + 
  facet_wrap(~Grazing) # function to separate
```

Save the plot as a .png
```{r}
ggsave("ThatCoolHistogramOfFruit.png")
```

